TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages

### 2021-03-25 article.tex
TTT: metodología, múltiples equipos

\en{We now analyze a more complex example in which the same four players participate in a multi-team game.}
\es{Ahora analizamos un ejemplo más complejo en el que los mismos cuatro jugadores participan en un juego de varios equipos.}
%
\en{The players are organized in three teams of different size: two teams with only one player, and the other with two players.}
\es{Los jugadores se organizan en tres equipos de diferente tamaño: dos equipos con un solo jugador, y el otro con dos jugadore.}
%
\en{The result has a single winning team and a tie between the other two losing teams.}
\es{El resultado tiene un único equipo ganador y un empate entre los otros dos equipos perdedores.}
%
\en{Unlike the previous example, we need to use a draw probability greater than zero.}
\es{A diferencia del ejemplo anterior, ahora necesitamos usar una probabilidad de empate mayor a cero.}
%
\begin{lstlisting}[backgroundcolor=\color{white},label=lst:game, caption={\en{Games with multiple teams of different sizes and the possibility of ties}\es{Juegos con multiples equipos de diferente tamaño y posibilidad de empates}}, belowskip=-1.0 \baselineskip, aboveskip=0.1cm]
\end{lstlisting}
\begin{paracol}{3}
\begin{lstlisting}[backgroundcolor=\color{julia}, belowskip=-0.77 \baselineskip]
ta = [p1]
tb = [p2, p3]
tc = [p4]
teams = [ta, tb, tc]
result = [1., 0., 0.]
\end{lstlisting}
  \switchcolumn
\begin{lstlisting}[backgroundcolor=\color{python}, belowskip=-0.77 \baselineskip]
ta = [p1]
tb = [p2, p3]
tc = [p4]
teams = [ta, tb, tc]
result = [1, 0, 0]
\end{lstlisting}
   \switchcolumn
\begin{lstlisting}[backgroundcolor=\color{r}, belowskip=-0.77 \baselineskip]
ta = c(p1)
tb = c(p2, p3)
tc = c(p4)
teams = list(ta, tb, tc)
result = c(1, 0, 0)
\end{lstlisting}  
\end{paracol}
\begin{lstlisting}[backgroundcolor=\color{all}]
g2 = Game(teams, result, p_draw=0.25)
\end{lstlisting}
%
\en{where \texttt{teams} contains the players distributed in different teams, while \texttt{result} now indicates the score obtained by each team.}
\es{donde \texttt{teams} contiene a los jugadores distribuidos en diferentes equipos, mientras que \texttt{result} indica ahora la puntuación obtenida por cada equipo.}
%
\en{The team with the highest score is the winner and the teams with the same score are tied.}
\es{El equipo con la mayor puntuación es el ganador y los equipos con misma puntuación están empatados.}
%
\en{In this way we can specify any outcome, including global draws.}
\es{De este modo podemos especificar cualquier resultado, incluidos empates globales.}
%
\en{The evidence and the posteriors can be queried in the same way as before.}
\es{La evidencia y el posterior se obtienen de la misma forma que hemos visto.}

@@

\subsection{\en{The team model and the exact solution}\es{El modelo de equipos y la solución exacta}}\label{sec:2vs2}

\en{TrueSkill also allows modeling team games.}
\es{TrueSkill también permite modelar partidas con equipos.}
%
\en{The model assumes that the team with the highest performance wins, $r = (t_i > t_j)$, where $t_i$ and $t_j$ represent the team performances.}
\es{El modelo supone que gana el equipo con mayor rendimiento, $r = (t_i > t_j)$, donde $t_i$ y $t_j$ representan los desempeños de los equipos.}
%
\en{In figure~\ref{fig:modelo_trueskill_2vs2} we show the factor graph.}
\es{En la figura~\ref{fig:modelo_trueskill_2vs2} mostramos la factorizaci\'on gr\'afica.} 
%
\begin{figure}[h!]
  \centering
  \scalebox{.9}{
  \tikz{

@@

\subsection{\en{Multiple teams}\es{Varios equipos}} \label{sec:iterative_posterior} 
%
\en{In this section we will see how to find the best approximation to the exact posterior in cases where we have more than two teams.}
\es{En esta secci\'on veremos como encontrar la mejor aproximaci\'on al posterior exacto en casos en los que tenemos m\'as de dos equipos.}
%
\en{Let's assume that $n$ agents, organized in $k$ teams $\{1, \dots, k\}$, participate in an event.}
\es{Supongamos que $n$ agentes, organizados en $k$ equipos $\{1, \dots, k\}$, participan de un evento.}
%
\en{The team assignment is represented by a partition of the set of agents, $A$, into $k$ non-overlapping subsets, $A_i$.}
\es{La asignaci\'on de equipos se representa como una partici\'on del conjunto de agentes, $A$, en $k$ subconjuntos disjuntos, $A_i$.}
%
\en{Due to the transitivity of the result, it is enough to evaluate $k-1$ distribution of differences $d_i$ between consecutive teams in the ranking.}
\es{Gracias a la transitividad de los resultados, es suficiente con evaluar $k-1$ distribuciones de diferencia $d_i$ entre equipos consecutivos en el ranking.}
%
\en{For that purpose we define the order of teams that arises from the observed result, $ o:= (o_1, \ dots, o_k) $, where $ o_1 $ indicates the winning team, and in general $ o_i = e $ indicates that the team $ e $ was located at position $ i $.}
\es{Para ese prop\'osito definimos el orden de equipos que surge del resultado observdo, $o := (o_1, \dots, o_k)$, donde $o_1$ indica el equipo ganador, y en general $o_i = e$ indica que el equipo $e$ qued\'o ubicado en la posici\'on $i$.}
%
\begin{figure}[h!]
  \centering
  \scalebox{.9}{
  \tikz{ %
        \node[factor] (fr) {} ;
        \node[const, above=of fr] (nfr) {$f_r$}; %
	\node[const, above=of nfr] (dfr) {\large $\mathbb{I}(d_i>0)$}; %
        \node[latent, left=of fr] (d) {$d_j$} ; %
        \node[factor, left=of d] (fd) {} ;
        \node[const, above=of fd] (nfd) {$f_d$}; %
        \node[const, above=of nfd] (dfd) {\large $\mathbb{I}(d_i=t_{o_i} - t_{o_{i+1}})$}; %

        \node[latent, left=of fd,xshift=-0.9cm] (t) {$t_e$} ; %
        \node[factor, left=of t] (ft) {} ;
        \node[const, above=of ft] (nft) {$f_t$}; %
        \node[const, above=of nft,xshift=0.5cm] (dft) {\large $\mathbb{I}(t_e = \sum_{i \in A_e} p_i)$}; %

        \node[latent, left=of ft] (p) {$p_i$} ; %
        \node[factor, left=of p] (fp) {} ;
        \node[const, above=of fp] (nfp) {$f_p$}; %
        \node[const, above=of nfp] (dfp) {\large $N(p_i|s_i,\beta^2)$}; %

        \node[latent, left=of fp] (s) {$s_i$} ; %
        \node[factor, left=of s] (fs) {} ;
        \node[const, above=of fs] (nfs) {$f_s$}; %
        \node[const, above=of nfs] (dfs) {\large $N(s_i|\mu_i,\sigma^2)$}; %

@@

        \plate {personas} {(p)(s)(fs)(nfs)(dfp)(dfs)} {$i \in A_e$}; %
        \node[invisible, below=of ft, yshift=-0.6cm] (inv_below_e) {};
	\node[invisible, above=of ft, yshift=1.1cm] (inv_above_e) {};
	\plate {equipos} {(personas) (t)(ft)(dft) (inv_above_e) (inv_below_e)} {$  \text{\en{Let $A$ be a partition of agents }\es{Sea $A$ una partici\'on de agentes } }$  \hspace{3cm} $0 < e \leq |A|$}; %
	\node[invisible, below=of fr, yshift=-0.6cm] (inv_below) {};
	\node[invisible, above=of fr, yshift=1.1cm] (inv_above) {};
	\plate {comparaciones} {(fd) (dfd) (d) (fr) (dfr) (inv_below) (inv_above)} {$o:=$\en{ observed order}\es{ orden observado} \hspace{1cm} $1 \leq i < |A|$};
    }  
    }
  \caption{
  \en{Factorization of the generic multi-team model.}
  \es{Factorizaci\'on del modelo de multiequipos gen\'erico.}
  %
  \en{Plates indicate replication.}
  \es{Las placas indican replicaci\'on.}
  %
  }
  \label{fig:factorGraph_trueskill}
\end{figure}
%
\en{In Figure ~\ref{fig:factorGraph_trueskill} we show the factorization of the general TrueSkill model.}
\es{En la figura~\ref{fig:factorGraph_trueskill} mostramos la factorizaci\'on del modelo general de TrueSkill.}
%
\en{Let's see how to solve a game with 3 teams.}
\es{Veamos como se resuelve un caso de 3 equipos.}
%
\en{For the users of the package there is no difference regarding the previous case.}
\es{Para los usuarios del paquete no hay ninguna diferencia respecto del caso anterior.}
%
\vspace{-0.6cm}
\begin{figure}[H]
\begin{lstlisting}[backgroundcolor=\color
{white},label=lst:multi_team_game, caption=\relax, belowskip=-1.5 \baselineskip, aboveskip=-0 \baselineskip]
\end{lstlisting}
\begin{subfigure}[t]{0.32\textwidth}
\begin{lstlisting}[backgroundcolor=\color{julia}]
team_a = [ r1 ]
team_b = [ r2, r3 ]
team_b = [ r4 ]
teams= [team_a,team_b,team_c]
result = [1,0,0]
g = Game(teams,result,p_draw)
p = posteriors(g)
\end{lstlisting} 
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\begin{lstlisting}[backgroundcolor=\color{python}]
team_a = [ r1 ]
team_b = [ r2, r3 ]
team_b = [ r4 ]
teams= [team_a,team_b,team_c]
result = [1,0,0]
g = Game(teams,result,p_draw)
p = g.posteriors()
\end{lstlisting}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\begin{lstlisting}[backgroundcolor=\color{r}]
teams = list()
teams$team_a = c(r1)
teams$team_b = c(r2, r3)
teams$team_c = c(r4)
result = c(1,0,0)
g = Game(teams,result,p_draw)
p = g$posteriors()
\end{lstlisting}   
\end{subfigure}
\end{figure}
\vspace{-0.6cm}
%
\en{In these cases it is impossible to perform a one-shot inference because of the mutual dependency between the distribution of difference, $p(d_i)$.}
\es{En estos caso es imposible realizar la inference de una sola pasada por la dependencia mutua entre las distribuciones de diferencia, $p(d_i)$.}
%
\en{The basic idea is to update repeatedly forward and backward all messages in the shortest path between any two marginals $p(d_i)$ until convergence, as shown in Figure~\ref{fig:ep_ts}.}
\es{La idea b\'asica es actualizar repetidamente hacia adelante y hacia atr\'as todos los mensajes en el camino m\'as corto entre dos marginales $p(d_i)$ hasta la convergencia, como se muestra en la figura~\ref{fig:ep_ts}.}
%
\begin{figure}[H]
  \centering
  \scalebox{.9}{
\tikz{ %        
        \node[factor, xshift=-5cm] (fta) {} ;
        \node[const, right=of fta] (nfta) {$f_{t_a}$}; %
        \node[latent, below=of fta,yshift=-0.5cm] (ta) {$t_a$} ; %

@@

        \path[draw, -latex, fill=black!50,sloped] (fd1) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize  \texttt{lhood\_lose\_tb}} (tb);

        \path[draw, -latex, fill=black!50,sloped] (tb) edge[bend left,draw=black!50] node[midway,below,color=black!75] {\scriptsize \texttt{ \ posterior\_lose\_tb}} (fd1);

        \path[draw, -latex, fill=black!50,sloped] (fd2) edge[bend right,draw=black!50] node[midway,above,color=black!75] {\scriptsize \texttt{lhood\_win\_tb}} (tb);

        \path[draw, -latex, fill=black!50,sloped] (tb) edge[bend right,draw=black!50] node[midway,below,color=black!75] {\scriptsize \texttt{posterior\_win\_tb}} (fd2);

        \path[draw, -latex, fill=black!50,sloped] (fta) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize \texttt{prior\_ta}} (ta);

        \path[draw, -latex, fill=black!50,sloped] (fr1) edge[bend left,draw=black!50] node[midway,above,color=black!75, rotate=180] {\scriptsize \texttt{lhood\_d1}} (d1);

        \path[draw, -latex, fill=black!50,sloped] (d1) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize \texttt{lhood\_d1\_approx}} (fd1);

        \path[draw, -latex, fill=black!50,sloped] (fd1) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize \texttt{prior\_d1}} (d1);

        \path[draw, -latex, fill=black!50,sloped] (tc) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize \texttt{lhood\_tc\_approx}} (ftc);

        %\path[draw, -latex, fill=black!50,sloped] (fr2) edge[bend left,draw=black!50] node[midway,above,color=black!75, rotate=180] {\scriptsize \textbf{5:} \emph{likelihood}$(d_{0})$} (d2);

        %\path[draw, -latex, fill=black!50,sloped] (fd2) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize \textbf{4:} \emph{prior}$(d_{0})$} (d2);
 \en{Factorization of a game with 3 teams.}
 \es{Factorizaci\'on de una partida con 3 equipos.}
 \en{We only show factors from the teams to the results.}
 \es{Mostramos s\'olo factores desde los equipos hasta los resultados.}
 \en{The names will be used to explain the iterative procedure known as loopy belief propagation.}
 \es{Los nombres se usar\'an para explicar el procedimiento iterativo conocido como \emph{loopy belief propagatiion}.}
\label{fig:ep_ts}
\en{First we define the Prior of the teams.}
\es{Primero definimos el prior de los equipos.}
{white},label=lst:team_prior, caption=\relax, belowskip=-1.0 \baselineskip, aboveskip=-0 \baselineskip]

@@

\en{Messages that are not yet defined are initialized with a neutral form, such as a Gaussian distribution with infinite variance.}

@@

{white},label=lst:init_lhood, caption=\relax, belowskip=-1.0 \baselineskip, aboveskip=-0 \baselineskip]

@@

@@

\en{We compute the margins for each comparison, $d_i$.}
\es{Calculamos el los margenes para cada comparaci\'on $d_1$.}
{white},label=lst:margin, caption=\relax, belowskip=-1.0 \baselineskip, aboveskip=-0 \baselineskip]
margin = compute_margin(p_draw, sqrt(3)*BETA)
\en{Let's start the iterative process by computing the messages of one distributions of difference, for example $d_1$.}
\es{Empezmos el proceso iterativo calculando una de las distribuciones de diferencia, por ejemplo $d_1$.}
{white},label=lst:d1, caption=\relax, belowskip=-1.0 \baselineskip, aboveskip=-0 \baselineskip]

@@

\en{The message \texttt{lhood\_d1\_approx} allows us to update the distribution of performance $t_b$.}
\es{El mensahe \texttt{lhood\_d1\_approx} nos permite actualizar la distribuci\'on de rendimietos $t_b$.}
{white},label=lst:tb_lose, caption=\relax, belowskip=-1.0 \baselineskip, aboveskip=-0 \baselineskip]

@@

\en{Then we compute the the messages of the next distribution of differences $d_2$.}
\es{Luego computamos los mensajes de la siguiente distirbuci\'on de diferencia $d_2$.}
{white},label=lst:d2, caption=\relax, belowskip=-1.0 \baselineskip, aboveskip=-0 \baselineskip]

@@

{white},label=lst:tb_win, caption=\relax, belowskip=-1.0 \baselineskip, aboveskip=-0 \baselineskip]

@@

{white},label=lst:te_side, caption=\relax, belowskip=-1.0 \baselineskip, aboveskip=-0 \baselineskip]

@@

{white},label=lst:lhood_te_approx, caption=\relax, belowskip=-1.0 \baselineskip, aboveskip=-0 \baselineskip]

@@

\en{As an example, we compute the posterior of player 2.}
\es{A modo de ejemplo, computamos el posterior del jugador 2.}
{white},label=lst:posterior_s2_approx, caption=\relax, belowskip=-1.0 \baselineskip, aboveskip=-0 \baselineskip]
prior2 = r2.N
ex = exclude(prior_tb,prior2)
prior2 = r2.N
ex = prior_tb.exclude(prior2)
prior2 = r2$N
ex = prior_tb$exclude(prior2)
team_b_without_s2 = ex
lhood_s2_approx = lhood_ta_approx - team_b_without_s2 
posterior_s2_approx = prior2 * lhood_s2_approx 

@@

        %\draw[bend right=90] (fs1) arc (s1) node[midway,above]{label};

>>>>

\en{We now analyze a more complex example in which the same four players participate in a multi-team game.}
\es{Ahora analizamos un ejemplo más complejo en el que los mismos cuatro jugadores participan en un juego de varios equipos.}
%
\en{The players are organized in three teams of different size: two teams with only one player, and the other with two players.}
\es{Los jugadores se organizan en tres equipos de diferente tamaño: dos equipos con un solo jugador, y el otro con dos jugadore.}
%
\en{The result has a single winning team and a tie between the other two losing teams.}
\es{El resultado tiene un único equipo ganador y un empate entre los otros dos equipos perdedores.}
%
\en{Unlike the previous example, we need to use a draw probability greater than zero.}
\es{A diferencia del ejemplo anterior, ahora necesitamos usar una probabilidad de empate mayor a cero.}
%
\begin{lstlisting}[backgroundcolor=\color{white},label=lst:multiple_team_game, caption={\en{Games with multiple teams of different sizes and the possibility of ties}\es{Juegos con multiples equipos de diferente tamaño y posibilidad de empates}}, belowskip=-1.0 \baselineskip, aboveskip=0.1cm]
\end{lstlisting}
\begin{paracol}{3}
\begin{lstlisting}[backgroundcolor=\color{julia}, belowskip=-0.77 \baselineskip]
ta = [p1]
tb = [p2, p3]
tc = [p4]
teams = [ta, tb, tc]
result = [1., 0., 0.]
\end{lstlisting}
  \switchcolumn
\begin{lstlisting}[backgroundcolor=\color{python}, belowskip=-0.77 \baselineskip]
ta = [p1]
tb = [p2, p3]
tc = [p4]
teams = [ta, tb, tc]
result = [1, 0, 0]
\end{lstlisting}
   \switchcolumn
\begin{lstlisting}[backgroundcolor=\color{r}, belowskip=-0.77 \baselineskip]
ta = c(p1)
tb = c(p2, p3)
tc = c(p4)
teams = list(ta, tb, tc)
result = c(1, 0, 0)
\end{lstlisting}  
\end{paracol}
\begin{lstlisting}[backgroundcolor=\color{all}]
g2 = Game(teams, result, p_draw=0.25)
\end{lstlisting}
%
\en{where \texttt{teams} contains the players distributed in different teams, while \texttt{result} now indicates the score obtained by each team.}
\es{donde \texttt{teams} contiene a los jugadores distribuidos en diferentes equipos, mientras que \texttt{result} indica ahora la puntuación obtenida por cada equipo.}
%
\en{The team with the highest score is the winner and the teams with the same score are tied.}
\es{El equipo con la mayor puntuación es el ganador y los equipos con misma puntuación están empatados.}
%
\en{In this way we can specify any outcome, including global draws.}
\es{De este modo podemos especificar cualquier resultado, incluidos empates globales.}
%
\en{The evidence and the posteriors can be queried in the same way as before.}
\es{La evidencia y el posterior se obtienen de la misma forma que hemos visto.}

@@

\subsection{\en{The exact solution of the team model}\es{La solución exacta del modelo de equipos}}\label{sec:2vs2}

\en{TrueSkill allows to estimate the skill of individuals even when they play in teams.}
\es{TrueSkill permite estimar la habilidad de los individuos incluso cuando estos juegan en equipo.}
%
\en{The model assumes that the team with the highest performance wins, $r = (t_i > t_j)$, where $t_i$ and $t_j$ represent the team performances.}
\es{El modelo supone que gana el equipo con mayor rendimiento, $r = (t_i > t_j)$, donde $t_i$ y $t_j$ representan los desempeños de los equipos.}
%
\en{In figure~\ref{fig:modelo_trueskill_2vs2} we show the factor graph.}
\es{En la figura~\ref{fig:modelo_trueskill_2vs2} mostramos la factorizaci\'on gr\'afica.} 
%
\begin{figure}[h!]
  \centering
  \scalebox{.9}{
  \tikz{

@@

\subsection{\en{Multiple teams}\es{Varios equipos}} \label{sec:iterative_posterior}

\en{In cases where there are more than two teams, a mutual dependence between the results forces us to implement an iterative algorithm to approximate the posterior.}
\es{Cuando estamos en presencia de m\'as de dos equipos, una dependencia mutua entre los resultados nos obliga a implementar un algoritmo iterativo para aproximar el posterior.}
%
\en{Let's assume that $k$ teams participate in an event.}
\es{Supongamos que $k$ equipos participan de un evento.}
%
\en{Due to the transitivity of the result, it is enough to evaluate $k-1$ differences $d_i$ between consecutive teams.}
\es{Gracias a la transitividad de los resultados, es suficiente con evaluar $k-1$ diferencias $d_i$ entre equipos consecutivos.}
%
\en{For this purpose we define a list, $o$, in which the teams are ordered according to the observed result, with $o_1$ the winning team, and in general $o_i$ representing the team placed in position $i$.}
\es{Para ese propósito definimos una lista, $o$, en la que los equipos están ordenados según el resultado observdo, con $o_1$ el equipo ganador ,y en general con $o_i$ el equipo ubicado en la posición $i$.}
%
\en{In Figure ~\ref{fig:factorGraph_trueskill} we show the factorization of the general TrueSkill model.}
\es{En la figura~\ref{fig:factorGraph_trueskill} mostramos la factorizaci\'on del modelo general de TrueSkill.}
%
\begin{figure}[h!]
  \centering
  \scalebox{.9}{
  \tikz{ %
        \node[factor] (fr) {} ;
        \node[const, above=of fr] (nfr) {$f_r$}; %
	\node[const, above=of nfr] (dfr) {\large $\mathbb{I}(d_j>0)$}; %
        \node[latent, left=of fr] (d) {$d_j$} ; %
        \node[factor, left=of d] (fd) {} ;
        \node[const, above=of fd] (nfd) {$f_d$}; %
        \node[const, above=of nfd] (dfd) {\large $\delta(d_j=t_{o_j} - t_{o_{j+1}})$}; %

        \node[latent, left=of fd,xshift=-0.9cm] (t) {$t_{o_j}$} ; %
        \node[factor, left=of t] (ft) {} ;
        \node[const, above=of ft] (nft) {$f_t$}; %
        \node[const, above=of nft,xshift=0.5cm] (dft) {\large $\delta(t_{o_j} = \sum_{i} p_i)$}; %

        \node[latent, left=of ft] (p) {$p_i$} ; %
        \node[factor, left=of p] (fp) {} ;
        \node[const, above=of fp] (nfp) {$f_p$}; %
        \node[const, above=of nfp] (dfp) {\large $\N(p_i|s_i,\beta^2)$}; %

        \node[latent, left=of fp] (s) {$s_i$} ; %
        \node[factor, left=of s] (fs) {} ;
        \node[const, above=of fs] (nfs) {$f_s$}; %
        \node[const, above=of nfs] (dfs) {\large $\N(s_i|\mu_i,\sigma^2)$}; %

@@

        \plate {personas} {(p)(s)(fs)(nfs)(dfp)(dfs)} {$T_{o_j}\equiv$ \en{composition of team $o_j$}\es{composición del equipo $o_j$} \hspace{0.5cm} $i \in T_{o_j}$}; %
        \node[invisible, below=of ft, yshift=-0.6cm] (inv_below_e) {};
	\node[invisible, above=of ft, yshift=1.1cm] (inv_above_e) {};
	\plate {equipos} {(personas) (t)(ft)(dft) (inv_above_e) (inv_below_e)} {$o\equiv$ \en{list of teams ordered according to the results }\es{lista de equiois ordenada de acuerdo los resultados }  \hspace{0.3cm} $1 \leq j \leq |o|$}; %
	\node[invisible, below=of fr, yshift=-0.7cm] (inv_below) {};
	\node[invisible, above=of fr, yshift=1.1cm] (inv_above) {};
	\plate {comparaciones} {(fd) (dfd) (d) (fr) (dfr) (inv_below) (inv_above)} {$1 \leq j < |o|$};
    }  
    }
  \caption{
  \en{General factor graph of the team model.}
  \es{Factorizaci\'on general del modelo de equipos.}
  %
  \en{The subscripts appearing at the bottom right of the plates indicate replication.}
  \es{Los subíndices que aparecen abajo a la derecha en las placas, indican replicaci\'on.}
  %
  \en{The $j$ subscript of the left plate opens the $k$ team performances, and the $i$ subscript of the inner plate displays their players.}
  \es{El subíndice $j$ de la placa izquierda abre los $k$ rendimientos de equipos, y el subíndice $i$ de la placa interna despliega sus jugadores.}
  %
  \en{The subscript $j$ of the right plate opens the $k-1$ comparisons between consecutive teams.}
  \es{El subíndice $j$ de la placa derecha abre los $k-1$ comparaciones entre equipos consecutivos.}
  }
  \label{fig:factorGraph_trueskill}
\end{figure}
%
\en{For a user of the package there is no difference regarding the previous case, as shown in code~\ref{lst:multiple_team_game}.}
\es{Para un usuario del paquete no hay ninguna diferencia respecto del caso anterior, como se puede ver en el código~\ref{lst:multiple_team_game}.}
%
\en{However, mathematically it is impossible to perform a one-shot inference because of the mutual dependency between the distribution of difference, $p(d_j)$.}
\es{Sin embargo, matemáticamente es imposible realizar la inference de una sola pasada por la dependencia mutua entre las distribuciones de diferencia, $p(d_j)$.}
%
\en{Let's look at the algorithm involved in solving a game with 3 teams.}
\es{Veamos el algoritmo involucrado en resolver una partida con 3 equipos.}
%
\en{The basic idea is to update repeatedly forward and backward all messages in the shortest path between any two marginals $p(d_j)$ until convergence.}
\es{La idea b\'asica es actualizar repetidamente hacia adelante y hacia atr\'as todos los mensajes en el camino m\'as corto entre dos marginales $p(d_j)$ hasta la convergencia.}
%
\en{Instead of using the message notation proposed by the sum-product algorithm, we name the messages as shown in Figure~\ref{fig:ep_ts}.}
\es{En vez de utilizar la notación de mensajes propuesta por el \emph{sum-product algorithm}, le ponemos nombres a los mensajes como se muestra en la figura~\ref{fig:ep_ts}.}
%
\begin{figure}[h!]
  \centering
  \scalebox{.9}{
\tikz{ %        
        \node[factor, xshift=-5cm] (fta) {} ;
        \node[const, right=of fta] (nfta) {$f_{t_a}$}; %
        \node[latent, below=of fta,yshift=-0.5cm] (ta) {$t_a$} ; %

@@

        \path[draw, ->, fill=black!50,sloped] (fd1) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize  \texttt{lhood\_lose\_tb}} (tb);

        \path[draw, ->, fill=black!50,sloped] (tb) edge[bend left,draw=black!50] node[midway,below,color=black!75] {\scriptsize \texttt{ \ posterior\_lose\_tb}} (fd1);

        \path[draw, ->, fill=black!50,sloped] (fd2) edge[bend right,draw=black!50] node[midway,above,color=black!75] {\scriptsize \texttt{lhood\_win\_tb}} (tb);

        \path[draw, ->, fill=black!50,sloped] (tb) edge[bend right,draw=black!50] node[midway,below,color=black!75] {\scriptsize \texttt{posterior\_win\_tb}} (fd2);

        \path[draw, ->, fill=black!50,sloped] (fta) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize \texttt{prior\_ta}} (ta);

        \path[draw, ->, fill=black!50,sloped] (fr1) edge[bend left,draw=black!50] node[midway,above,color=black!75, rotate=180] {\scriptsize \texttt{lhood\_d1}} (d1);

        \path[draw, ->, fill=black!50,sloped] (d1) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize \texttt{lhood\_d1\_approx}} (fd1);

        \path[draw, ->, fill=black!50,sloped] (fd1) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize \texttt{prior\_d1}} (d1);

        \path[draw, ->, fill=black!50,sloped] (tc) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize \texttt{lhood\_tc}} (ftc);

        %\path[draw, ->, fill=black!50,sloped] (fr2) edge[bend left,draw=black!50] node[midway,above,color=black!75, rotate=180] {\scriptsize \textbf{5:} \emph{likelihood}$(d_{0})$} (d2);

        %\path[draw, ->, fill=black!50,sloped] (fd2) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize \textbf{4:} \emph{prior}$(d_{0})$} (d2);

} 
}
\caption{
 \en{Factorization of a game with 3 teams.}
 \es{Factorizaci\'on de una partida con 3 equipos.}
 %
 \en{We only show factors from the teams to the results.}
 \es{Mostramos s\'olo factores desde los equipos hasta los resultados.}
 %
 \en{The names will be used to explain the iterative procedure known as loopy belief propagation.}
 \es{Los nombres se usar\'an para explicar el procedimiento iterativo conocido como \emph{loopy belief propagatiion}.}
}
\label{fig:ep_ts}
\end{figure}

\en{We will solve the convergence corresponding to the example shown at code~\ref{lst:multiple_team_game}.}
\es{Vamos a resolver la convergencia correpodientes al ejemplo del código~\ref{lst:multiple_team_game}.}
\en{First we define the prior performance of the teams.}
\es{Primero definimos el desempeño a prior de los equipos.}
\begin{lstlisting}[backgroundcolor=\color{all},belowskip=0.1cm]

@@

\en{Messages that are not yet defined must be initialized with a neutral form, such as a Gaussian distribution with infinite variance.}

@@

@@

\begin{lstlisting}[backgroundcolor=\color{all},belowskip=0.1cm]

@@

\en{We compute the margins for each comparison, $d_j$.}
\es{Calculamos el los margenes para cada comparaci\'on $d_j$.}
\en{Since there are 3 players in both comparisons, we adjust both margins to that size.}
\es{Como en ambas comparaciones hay 3 jugadores, ajustamos ambos margenes a ese tamaño.}
\begin{lstlisting}[backgroundcolor=\color{all},belowskip=0.1cm]
margin = compute_margin(p_draw, sqrt(3)*beta)
\en{Let's start the iterative process by approximating the distributions $d_1$.}
\es{Empezmos el proceso iterativo aproximando la distribuciones $d_1$.}
\begin{lstlisting}[backgroundcolor=\color{all},belowskip=0.1cm, label=lst:d1, caption={\en{Approximating the distribution $d_1$ with the last messages of $t_b$}\es{Aproximando la distribución $d_1$ con los últimos mensajes de $t_b$}},aboveskip=0.0 \baselineskip]

@@

\en{The message \texttt{lhood\_d1\_approx} allows us to update the distribution of performance $p(t_b)$.}
\es{El mensahe \texttt{lhood\_d1\_approx} nos permite actualizar la distribuci\'on de rendimietos $p(t_b)$.}
\begin{lstlisting}[backgroundcolor=\color{all},label=lst:tb_lose, caption={\en{Updating the messages of $t_b$  with the last approximation of $d_1$}\es{Actualizando la distribución $t_b$ con la última aproximación de $d_1$}},aboveskip=0.0 \baselineskip]

@@

\en{Then we approximate the distribution $d_2$ using the updated message \texttt{lhood\_lose\_tb}.}
\es{Luego aproximamos la distribución $d_2$ usando el mensaje \texttt{lhood\_lose\_tb } actualizado.}
\begin{lstlisting}[backgroundcolor=\color{all},label=lst:d2, caption={\en{Approximating de distribution $d_2$ with the last messages of $t_b$}\es{Aproximando la distribución $d_2$ con lo últimos mensajes de $t_b$}},aboveskip=0.0 \baselineskip]

@@

\begin{lstlisting}[backgroundcolor=\color{all},label=lst:tb_win, caption={\en{Updating la distribución $t_b$ with the approximation of $d_2$}\es{Actualizando la distribución $t_b$  con la aproximación de $d_2$}},aboveskip=0.0 \baselineskip]

@@

@@

@@

% \en{As an example, we compute the posterior of player 2.}
% \es{A modo de ejemplo, computamos el posterior del jugador 2.}
% \begin{lstlisting}[backgroundcolor=\color
% {white},label=lst:posterior_s2_approx, caption=\relax, belowskip=-1.0 \baselineskip, aboveskip=-0 \baselineskip]
% \begin{lstlisting}[backgroundcolor=\color{julia},belowskip=-0.77 \baselineskip]
% prior2 = r2.N
% ex = exclude(prior_tb,prior2)
% \begin{lstlisting}[backgroundcolor=\color{python},belowskip=-0.77 \baselineskip]
% prior2 = r2.N
% ex = prior_tb.exclude(prior2)
% \begin{lstlisting}[backgroundcolor=\color{r},belowskip=-0.77 \baselineskip]
% prior2 = r2$N
% ex = prior_tb$exclude(prior2)
% \begin{lstlisting}[backgroundcolor=\color{all}]
% team_b_without_s2 = ex
% lhood_s2_approx = lhood_ta_approx - team_b_without_s2 
% posterior_s2_approx = prior2 * lhood_s2_approx 

@@

%         %\draw[bend right=90] (fs1) arc (s1) node[midway,above]{label};
